### 2016-06-27 publications/Journal/6-conclusions.tex
First set of revisions and fixes.
Signed-off-by: Ben Cardoen <bencardoen@gmail.com>
Conclusion.
Signed-off-by: Ben Cardoen <bencardoen@gmail.com>

Future work is possible in several directions.
Firstly, our implementation of optimistic synchronization should be more tolerant to low-memory situations.
In its current state, simulation will simply halt with an out-of-memory error.
Having simulation control, which can throttle the speed of nodes that use up too much memory, has been shown to work in these situations~\cite{FujimotoBook}.
Faster GVT implementations, such as those presented by~\cite{Fujimoto:1997:CGV:268403.268404} and~\cite{Bauer:2005:SND:1069810.1070159}, might further help to minimize this problem.
Secondly, the idea of activity can be implemented for our simulation kernels, making it possible to dynamically switch between conservative and optimistic synchronization when behavioural changes are detected.
Thirdly, activity algorithms, as already implemented by PythonPDEVS, can also be implemented in dxex, to determine how they influence simulation performance.
Finally automatic allocation is possible by analysis of the connections between models. This information is already used in dxex to determine the blocking order for conservative synchronization and in the directconnect algorithm. A graph algorithm that distributes models while avoiding cycles in the resulting kernels topology could be used to maximize parallel speedup in either optimistic or conservative synchronization.

>>>>

Future work is possible in several directions.
Firstly, our implementation of optimistic synchronization should be more tolerant to low-memory situations.
In its current state, simulation will simply halt with an out-of-memory error.
Having simulation control, which can throttle the speed of nodes that use up too much memory, has been shown to work in these situations~\cite{FujimotoBook}.
Faster GVT implementations, such as those presented by~\cite{Fujimoto:1997:CGV:268403.268404} and~\cite{Bauer:2005:SND:1069810.1070159}, might further help to minimize this problem.
Secondly, the runtime switching between synchronization protocols can be driven using machine learning techniques. The simulation engine is already capable of collecting data to inform such a process.
Thirdly, activity algorithms, as already implemented by PythonPDEVS, can also be implemented in dxex, to determine how they influence simulation performance.
Finally automatic allocation is possible by analysis of the connections between models. This information is already used in dxex to construct the dependency graph in conservative synchronization. A graph algorithm that distributes models while avoiding cycles in the resulting kernel topology could be used to offer a parallel speedup in either optimistic or conservative synchronization, or serve as a default parallel allocation scheme that can be improved by the user.
